Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
better

We plan to solicit feedback on the design of this experiment at the HotPETs 2015 workshop.
Specifically, we would like a reliable way to target the testing of 
specific transports. Given that the average user does not have domain knowledge of 
what transports are for Tor, we wonder whether there is anything to infer from users' selection,
or whether they try transports at random?

>>>>

We plan to solicit feedback on the design of this experiment at the HotPETs 2015 workshop.
Specifically, we would like a reliable way to target the testing of 
specific transports. Given that the average user does not have domain knowledge of 
what transports are for Tor, we wonder whether there is anything to infer from users' selection,
or whether they try transports at random.
